%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Student Association of NTU Electrical Engineering} % Organization/group
    {Director of Information Department} % Affiliation/role
    {} % Location
    {Sep. 2018 - Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Lead a team of 20 to build, design and maintain software infrastructure systems that serves all our students in the department.}
        \item {Our members won 1st in software section and 2nd in hardware section at Meichu Hackathon.}
        \item {Create web game \textit{Foop} for 2018 EEnight and io game \textit{losEEr.io}, \textit{frEEstyle.io} for 2018 2017 EEweek.} \href{https://github.com/ByronHsu/Foop}{\textcolor{red}{[Foop]}} \href{https://github.com/ByronHsu/losEEr.io}{\textcolor{red}{[losEEr.io]}} \href{https://github.com/HowardMHJuan/2017EEweek}{\textcolor{red}{[frEEstyle.io]}}
        \item {Lead projects \textit{Course System}, \textit{Student Association Website}, \textit{NTUEE+} for the student association.} \href{https://github.com/NTUEEInfoDep}{\textcolor{red}{[Github organization]}}
        \item {Hold courses on frontend-development, server-management and algorithm for the members.}
      \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {NTUEE CAMP ELOLVE \href{https://byronhsu.github.io/2019eecamp/}{\textcolor{red}{[website]}}} % Organization/group
    {President} % Affiliation/role
    {} % Location
    {Jun. 2019 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {NTUEE Camp is the most prestigious student camp in Taiwan with 120+ staff members.}
        \item {We welcome 120 high school students (selected from 1000+ applications) for intensive hacking company visiting (Google, Delta) and various group activities (dancing, drama performance)}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
