%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {DEEP LEARNING RESEARCH INTERN} % Job title
    {NVIDIA Technology} % Organization
    {Taipei, Taiwan} % Location
    {Nov. 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supervised by Dr. Colleen Ruan. Focused on \textbf{Systematic Evolution of Ligands by Exponential Enrichment (SELEX)} optimization by deep learning to find high-affinity DNA aptamers to a certain target ligand.}
        \item {Integrated Bayesian Optimization with Convolutional Neural Network(CNN) to yield better experimental results.}
      \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
\cventry
    {UNDERGRADUATE RESEARCHER} % Job title
    {Vision \& Learning Lab, NTU} % Organization
    {Taipei, Taiwan} % Location
    {Sep. 2018 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supervised by Prof. Yu-Chiang Frank Wang. Proposed a \textbf{state-of-the-art unsupervised fisheye image rectification method.}}
        \item {\textbf{Co-first author of \textit{“Self-Supervised Deep Learning for Fisheye Image Rectification”}, in submission to IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP 2020).}}
      \end{cvitems}
    }

% %---------------------------------------------------------


%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {XiaoMi Technology} % Organization
    {Beijing, China} % Location
    {Jul. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participated in an open-source project MACE, a deep learning inference framework optimized for mobile heterogeneous platforms.}
        \item {Configured cross-platform compatibility with Travis CI.}
      \end{cvitems}
    }
%---------------------------------------------------------

\end{cventries}
