%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Open-Source Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Life as a git. Commit on your life! \href{https://github.com/ByronHsu/life-commit}{ \textcolor{red}{[Github Link]} }} % subtitle
    {Life-commit \textcolor{red}{(850 stars, Github-trending-repository)}} % Title
    {} % Location
    {Jan. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of projects
        \item {Life-Commit is a cli tool that allows you to build your own life branch using Terminal, also supporting the function to visualize local commits as a static webpage in one click.}
        \item {Selected as top-45 amazing node.js projects for 2018 on Mybridge@Medium.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Blink and lose. \href{https://github.com/ByronHsu/Never-Blink}{ \textcolor{red}{[Github Link]} }} % subtitle
    {Never-Blink \textcolor{red}{(450 stars, Github-trending-repository)}} % Title
    {} % Location
    {Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of projects
        \item {A online game that you can randomly connect to a player around the world and challenge him/her for a game of no blinking.}
        \item {Hit the headline of hackernews.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {An Elegant Visualizer for And-Inverter Graph \href{https://github.com/ByronHsu/AAG-Visualizer}{ \textcolor{red}{[Github Link]} }} % subtitle
    {AAG-visualizer \textcolor{red}{(75 stars)}} % Title
    {} % Location
    {Jan. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of projects
        \item {Because of the DSnP course, in order to debug, students are forced to consume time and paper graphing circuits from indecipherable aag files. To relief the situation, I made a online AAG-visualizer, which easily transforms the uploaded files into graphs.}
        \item {The project received a lot of praise from both course takers and Taiwan Frontend Club, with more than 75 stars on Github.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
